---
title: "Bayesian Linear Mixed Effects Models"
author: "Clemens Pilcher and Jack Jewson"
date: "20 Nov 2024"
output: html_document
---

## Preamble {.tabset}

### Working directory

+ Change this to be the directory that the stan files are saved in 

```{r setwd, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

my_dir <- "C:/Users/jjew0003/Documents/BarcelonaProjects/SufficientStatistics/RandomEffects"


```

### Packages

Loading the required packages.

```{r packages, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

library(rstan)
rstan_options(auto_write = TRUE)

library(microbenchmark)
library(brms)

library(rstanarm)

library(ggplot2)
library(ggpubr)
```


### stan

```{r stan, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

setwd(my_dir)

#http://discourse.mc-stan.org/t/stan-recompile-to-avoid-r-from-crashing/2631
LinearMixedEffectsModels_naive_stan <- stan_model(file="LinearMixedEffectsModels_vectorised.stan")
LinearMixedEffectsModels_brms_stan <- stan_model(file="LinearMixedEffectsModels_brms.stan")
LinearMixedEffectsModels_SuffStat_stan <- stan_model(file="LinearMixedEffectsModels_SuffStat.stan")

```

## n = 100, p = 10, J = 5

### Simulating Data

```{r sim_data_n100_p5_J5, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

# Set seed for reproducibility
set.seed(123)

# Number of observations
n <- 100
# Number of predictors
p <- 5
# Number of groups
J <- 5

# Jenerate random predictors
X <- matrix(rnorm(n * p), n, p)

# Define true coefficients
beta <- c(1, 2, -1, rep(0, p - 3))  # Only some predictors are non-zero

# Jenerate group indicators
group <- sample(1:J, n, replace = TRUE)
# Jenerate group-level effects
group_intercepts <- rnorm(J, mean = 0, sd = 1)
random_effects <- group_intercepts[group]

# Jenerate response variable
Y <- drop(X %*% beta + random_effects + rnorm(n))



```

### BRMS code

```{r brms, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}


# Create the data frame
data_brms <- data.frame(
  Y = Y,
  group = group,
  N = n,
  P = p
)

# Add the predictors to the data frame
for (i in 1:p) {
  col_name <- paste0("X", i)
  data_brms[[col_name]] <- X[, i]
}

# Define the mixed-effects formula
# Fixed effects for predictors and random intercept for groups
formula_mixed <- bf(Y ~ X1 + X2 + X3 + X4 + X5 + (1 | group) + 0)

# Fit the mixed-effects model using `brms`
fit <- brm(formula_mixed, data = data_brms, iter = 1, refresh = 0, silent = 0, prior = prior(normal(0, 10), class = b))

# Display the Stan code for the fitted model
stancode(fit)


```

### Vectorised Implementation

```{r LinearMixedEffectsModels_naive_stan_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_naive_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)

LinearMixedEffectsModels_naive_sampling <- sampling(object = LinearMixedEffectsModels_naive_stan, data = LinearMixedEffectsModels_naive_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, seed = 123, control = list(adapt_delta = 0.95)

)
LinearMixedEffectsModels_naive_params <- extract(LinearMixedEffectsModels_naive_sampling)

```


### BRMS

```{r LinearMixedEffectsModels_brms_stan_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_brms_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group, M_1 = 1, Z_1_1 = rep(1, n), prior_only = FALSE)# Z_1_1 is 1 as this is a random intercept model

LinearMixedEffectsModels_brms_sampling <- sampling(object = LinearMixedEffectsModels_brms_stan, data = LinearMixedEffectsModels_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, seed = 123, control = list(adapt_delta = 0.95)

)
LinearMixedEffectsModels_brms_params <- extract(LinearMixedEffectsModels_brms_sampling)

LinearMixedEffectsModels_brms_sampling_params <- rstan::get_sampler_params(LinearMixedEffectsModels_brms_sampling)

colMeans(LinearMixedEffectsModels_brms_sampling_params[[1]])

```

### sufficieint statistics

```{r LinearMixedEffectsModels_SuffStat_stan_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_SuffStat_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)

LinearMixedEffectsModels_SuffStat_sampling <- sampling(object = LinearMixedEffectsModels_SuffStat_stan, data = LinearMixedEffectsModels_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, seed = 123, control = list(adapt_delta = 0.95)

)
LinearMixedEffectsModels_SuffStat_params <- extract(LinearMixedEffectsModels_SuffStat_sampling)



```

### rstanarm

https://mc-stan.org/users/documentation/case-studies/tutorial_rstanarm.html - Section 3

```{r LinearMixedEffectsModels_rstanarm_stan_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  group = group,
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)

LinearMixedEffectsModels_rstanarm_sampling <-
  stan_lmer(
    Y ~ X + (1 | group) + 0,
    data = data_rstanarm,
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    adapt_delta = 0.95,
    seed = 123
  )

prior_summary(object = LinearMixedEffectsModels_rstanarm_sampling)

LinearMixedEffectsModels_rstanarm_params <- as.matrix(LinearMixedEffectsModels_rstanarm_sampling)

```

### Posterior Comparison

```{r LinearMixedEffectsModels_brms_SuffStat_stan_n100_p10_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

for(j in 1:p){
  plot(density(LinearMixedEffectsModels_naive_params$b[,j]), xlab = paste("beta", j), ylab = "Density", lwd = 3)
  lines(density(LinearMixedEffectsModels_brms_params$b[,j]), lwd = 3, col = "darkgrey")
  lines(density(LinearMixedEffectsModels_SuffStat_params$b[,j]), lwd = 3, col = "pink")
  lines(density(LinearMixedEffectsModels_rstanarm_params[,j]), lwd = 3, col = "brown")
}

for(j in 1:J){
  plot(density(LinearMixedEffectsModels_naive_params$z_1[,j]), xlab = paste("z", j), ylab = "Density", lwd = 3)
  lines(density(LinearMixedEffectsModels_brms_params$r_1_1[,j]), lwd = 3, col = "darkgrey")
  lines(density(LinearMixedEffectsModels_SuffStat_params$r_1_1[,j]), lwd = 3, col = "pink")
  lines(density(LinearMixedEffectsModels_rstanarm_params[,p+j]), lwd = 3, col = "brown")
}


plot(density(LinearMixedEffectsModels_naive_params$sigma), xlab = "sigma", ylab = "Density", lwd = 3)
lines(density(LinearMixedEffectsModels_brms_params$sigma), lwd = 3, col = "darkgrey")
lines(density(LinearMixedEffectsModels_brms_SuffStat_params$sigma), lwd = 3, col = "pink")
lines(density(LinearMixedEffectsModels_rstanarm_params[,p+J+1]), lwd = 3, col = "brown")


plot(density(LinearMixedEffectsModels_naive_params$sd_1), xlab = "sd_1", ylab = "Density", lwd = 3)
lines(density(LinearMixedEffectsModels_brms_params$sd_1), lwd = 3, col = "darkgrey")
lines(density(LinearMixedEffectsModels_brms_SuffStat_params$sd_1), lwd = 3, col = "pink")
lines(density(LinearMixedEffectsModels_rstanarm_params[,p+J+2]), lwd = 3, col = "brown")
```

```{r LinearMixedEffectsModels_brms_SuffStat_stan_n100_p10_diag_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
#par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
#par(mgp = c(2.15, 1, 0))
#par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)
par(mar = c(4, 4.3, 0.5, 0.5)) # bottom, left, top, right
par(mgp = c(2.75, 1.05, 0))
par(cex.lab = 1.875, cex.axis = 1.875, cex.main = 1.875)

library(paletteer)
greys <- paletteer_d("RColorBrewer::Jreys")

for(j in 1:p){
  plot(density(LinearMixedEffectsModels_naive_params$b[,j]), xlab = paste0("$\\beta_{", j, "}$"), ylab = "Density", lwd = 4, col = greys[3], main = "")#, main = paste0("Linear mixed effects model $n = 100$ $p = 5$ $J = 5$"))
  lines(density(LinearMixedEffectsModels_brms_params$b[,j]), lwd = 4, col = greys[9], lty = 2)
  lines(density(LinearMixedEffectsModels_SuffStat_params$b[,j]), lwd = 4, col = greys[5], lty = 3)
  lines(density(LinearMixedEffectsModels_rstanarm_params[,j]), lwd = 4, col = greys[7], lty = 4)
  if(j == 1){
    legend("topleft", c("brms", "rstanarm", "suff-stat", "vect"), col = c(greys[9], greys[7], greys[5], greys[3]), lwd = rep(4, 4), lty = c(2, 4, 3, 1), bty = "n", cex = 1.5)
  }
}

for(j in 1:J){
  plot(density(LinearMixedEffectsModels_naive_params$z_1[,j]), xlab = paste0("$u_{", j, "}$"), ylab = "Density", lwd = 4, col = greys[3], main = "")#, main = paste0("Linear mixed effects model $n = 100$ $p = 5$ $J = 5$"))
  lines(density(LinearMixedEffectsModels_brms_params$r_1_1[,j]), lwd = 4, col = greys[9], lty = 2)
  lines(density(LinearMixedEffectsModels_SuffStat_params$r_1_1[,j]), lwd = 4, col = greys[5], lty = 3)
  lines(density(LinearMixedEffectsModels_rstanarm_params[,p+j]), lwd = 4, col = greys[7], lty = 4)
}


plot(density(LinearMixedEffectsModels_naive_params$sigma), xlab = "$\\sigma$", ylab = "Density", lwd = 4, col = greys[3], main = "")#, main = paste0("Linear mixed effects model $n = 100$ $p = 5$ $J = 5$"))
lines(density(LinearMixedEffectsModels_brms_params$sigma), lwd = 4, col = greys[9], lty = 2)
lines(density(LinearMixedEffectsModels_SuffStat_params$sigma), lwd = 4, col = greys[5], lty = 3)
lines(density(LinearMixedEffectsModels_rstanarm_params[,p+J+1]), lwd = 4, col = greys[7], lty = 4)


plot(density(LinearMixedEffectsModels_naive_params$sd_1), xlab = "$\\sigma_u$", ylab = "Density", lwd = 4, col = greys[3], main = "")#, main = paste0("Linear mixed effects model $n = 100$ $p = 5$ $J = 5$"))
lines(density(LinearMixedEffectsModels_brms_params$sd_1), lwd = 4, col = greys[9], lty = 2)
lines(density(LinearMixedEffectsModels_SuffStat_params$sd_1), lwd = 4, col = greys[7], lty = 3)
lines(density(LinearMixedEffectsModels_rstanarm_params[,p+J+2]), lwd = 4, col = greys[7], lty = 4)
```

## microbench comparison - n100, p5, J5

### Simulating Data

```{r mbm_sim_data_n100_p5_J5, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

# Set seed for reproducibility
set.seed(123)

# Number of observations
n <- 100
# Number of predictors
p <- 5
# Number of groups
J <- 5

# Jenerate random predictors
X <- matrix(rnorm(n * p), n, p)

# Define true coefficients
beta <- c(1, 2, -1, rep(0, p - 3))  # Only some predictors are non-zero

# Jenerate group indicators
group <- sample(1:J, n, replace = TRUE)
# Jenerate group-level effects
group_intercepts <- rnorm(J, mean = 0, sd = 1)
random_effects <- group_intercepts[group]

# Jenerate response variable
Y <- drop(X %*% beta + random_effects + rnorm(n))


# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  group = group,
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)


```


```{r mbm_LinearMixedEffectsModels_stan_n100_p5_J5, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_naive_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)
LinearMixedEffectsModels_brms_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group, M_1 = 1, Z_1_1 = rep(1, n), prior_only = FALSE)
LinearMixedEffectsModels_SuffStat_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)

REM_mbm_n100_p5_J5 <- microbenchmark(
Vectorised = sampling(object = LinearMixedEffectsModels_naive_stan, data = LinearMixedEffectsModels_naive_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
BRMS = sampling(object = LinearMixedEffectsModels_brms_stan, data = LinearMixedEffectsModels_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
SuffStat = sampling(object = LinearMixedEffectsModels_SuffStat_stan, data = LinearMixedEffectsModels_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)),
rstandarm = LinearMixedEffectsModels_rstanarm_sampling <-
  stan_lmer(
    Y ~ X + (1 | group) + 0,
    data = data_rstanarm,
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    adapt_delta = 0.95,
    refresh = 0
  ),
times = 25, unit = "seconds"
)

```

```{r mbm_LinearMixedEffectsModels_stan_n100_p5_J5_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

REM_mbm_n100_p5_J5

```

## microbench comparison - n1000, p5_J5

### Simulating Data

```{r mbm_sim_data_n1000_p5_J5, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

# Set seed for reproducibility
set.seed(123)

# Number of observations
n <- 1000
# Number of predictors
p <- 5
# Number of groups
J <- 5

# Jenerate random predictors
X <- matrix(rnorm(n * p), n, p)

# Define true coefficients
beta <- c(1, 2, -1, rep(0, p - 3))  # Only some predictors are non-zero

# Jenerate group indicators
group <- sample(1:J, n, replace = TRUE)
# Jenerate group-level effects
group_intercepts <- rnorm(J, mean = 0, sd = 1)
random_effects <- group_intercepts[group]

# Jenerate response variable
Y <- drop(X %*% beta + random_effects + rnorm(n))


# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  group = group,
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)


```

### BRMS

```{r LinearMixedEffectsModels_brms_stan_n1000_p5_J5, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_brms_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group, M_1 = 1, Z_1_1 = rep(1, n), prior_only = FALSE)# Z_1_1 is 1 as this is a random intercept model

LinearMixedEffectsModels_brms_sampling <- sampling(object = LinearMixedEffectsModels_brms_stan, data = LinearMixedEffectsModels_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, seed = 123, control = list(adapt_delta = 0.95)

)
LinearMixedEffectsModels_brms_params <- extract(LinearMixedEffectsModels_brms_sampling)

LinearMixedEffectsModels_brms_sampling_params <- rstan::get_sampler_params(LinearMixedEffectsModels_brms_sampling)

colMeans(LinearMixedEffectsModels_brms_sampling_params[[1]])

```


```{r mbm_LinearMixedEffectsModels_stan_n1000_p5_J5, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_naive_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)
LinearMixedEffectsModels_brms_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group, M_1 = 1, Z_1_1 = rep(1, n), prior_only = FALSE)
LinearMixedEffectsModels_SuffStat_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)

REM_mbm_n1000_p5_J5 <- microbenchmark(
Vectorised = sampling(object = LinearMixedEffectsModels_naive_stan, data = LinearMixedEffectsModels_naive_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
BRMS = sampling(object = LinearMixedEffectsModels_brms_stan, data = LinearMixedEffectsModels_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
SuffStat = sampling(object = LinearMixedEffectsModels_SuffStat_stan, data = LinearMixedEffectsModels_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)),
rstandarm = LinearMixedEffectsModels_rstanarm_sampling <-
  stan_lmer(
    Y ~ X + (1 | group) + 0,
    data = data_rstanarm,
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,,
    adapt_delta = 0.95,
    refresh = 0
  ),
times = 25, unit = "seconds"
)


```

```{r mbm_LinearMixedEffectsModels_stan_n1000_p5_J5_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

REM_mbm_n1000_p5_J5

```

## microbench comparison - n10000, p5_J5

### Simulating Data

```{r mbm_sim_data_n10000_p5_J5, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

# Set seed for reproducibility
set.seed(123)

# Number of observations
n <- 10000
# Number of predictors
p <- 5
# Number of groups
J <- 5

# Jenerate random predictors
X <- matrix(rnorm(n * p), n, p)

# Define true coefficients
beta <- c(1, 2, -1, rep(0, p - 3))  # Only some predictors are non-zero

# Jenerate group indicators
group <- sample(1:J, n, replace = TRUE)
# Jenerate group-level effects
group_intercepts <- rnorm(J, mean = 0, sd = 1)
random_effects <- group_intercepts[group]

# Jenerate response variable
Y <- drop(X %*% beta + random_effects + rnorm(n))

# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  group = group,
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)


```


```{r mbm_LinearMixedEffectsModels_stan_n10000_p5_J5, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_naive_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)
LinearMixedEffectsModels_brms_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group, M_1 = 1, Z_1_1 = rep(1, n), prior_only = FALSE)
LinearMixedEffectsModels_SuffStat_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)

REM_mbm_n10000_p5_J5 <- microbenchmark(
Vectorised = sampling(object = LinearMixedEffectsModels_naive_stan, data = LinearMixedEffectsModels_naive_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
BRMS = sampling(object = LinearMixedEffectsModels_brms_stan, data = LinearMixedEffectsModels_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
SuffStat = sampling(object = LinearMixedEffectsModels_SuffStat_stan, data = LinearMixedEffectsModels_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)),
rstandarm = LinearMixedEffectsModels_rstanarm_sampling <-
  stan_lmer(
    Y ~ X + (1 | group) + 0,
    data = data_rstanarm,
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    adapt_delta = 0.95,
    refresh = 0
  ),
times = 25, unit = "seconds"
)



```

```{r mbm_LinearMixedEffectsModels_stan_n10000_p5_J5_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

REM_mbm_n10000_p5_J5

```

```{r mbm_LinearMixedEffectsModels_stan_final_plot_N, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

REM_mbm_n100_p5_J5_summary <- summary(REM_mbm_n100_p5_J5)

REM_mbm_n100_p5_J5_summary[["n"]] <- 100
REM_mbm_n100_p5_J5_summary[["J"]] <- 5

REM_mbm_n1000_p5_J5_summary <- summary(REM_mbm_n1000_p5_J5)

REM_mbm_n1000_p5_J5_summary[["n"]] <- 1000
REM_mbm_n1000_p5_J5_summary[["J"]] <- 5

REM_mbm_n10000_p5_J5_summary <- summary(REM_mbm_n10000_p5_J5)

REM_mbm_n10000_p5_J5_summary[["n"]] <- 10000
REM_mbm_n10000_p5_J5_summary[["J"]] <- 5

plot_df_summary <- dplyr::bind_rows(REM_mbm_n100_p5_J5_summary, REM_mbm_n1000_p5_J5_summary, REM_mbm_n10000_p5_J5_summary)

plot_df_summary["expr"] <- rep(c("vectorised", "brms", "sufficient statistics", "rstanarm"), 3)


REM_plot_N <- ggplot(plot_df_summary, aes(x = factor(n), y = median, colour = expr)) +
    geom_crossbar(aes(ymin = min, ymax = max), position = position_dodge(0.5)) + 
    labs(title = "Linear mixed effects model: $p = 5$, $J = 5$",
         x = "$n$",
         y = "Time (seconds)") +
    theme_minimal() +
    scale_color_brewer("Method", palette = "Set1") +
    theme(legend.position = "bottom")

REM_plot_N

REM_plot_N_log <- ggplot(plot_df_summary, aes(x = factor(n), y = log(median), colour = expr)) +
    geom_crossbar(aes(ymin = log(min), ymax = log(max)), position = position_dodge(0.5)) + 
    labs(title = "Linear mixed effects model: $p = 5$, $J = 5$",
         x = "$n$",
         y = "log-Time (log-seconds)") +
    theme_minimal() +
    scale_color_brewer("Method", palette = "Set1") +
    theme(legend.position = "bottom")

REM_plot_N_log



```


## microbench comparison - n1000, p5 J50

### Simulating Data

```{r mbm_sim_data_n1000_p5_J50, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

# Set seed for reproducibility
set.seed(123)

# Number of observations
n <- 1000
# Number of predictors
p <- 5
# Number of groups
J <- 50

# Jenerate random predictors
X <- matrix(rnorm(n * p), n, p)

# Define true coefficients
beta <- c(1, 2, -1, rep(0, p - 3))  # Only some predictors are non-zero

# Jenerate group indicators
group <- sample(1:J, n, replace = TRUE)
# Jenerate group-level effects
group_intercepts <- rnorm(J, mean = 0, sd = 1)
random_effects <- group_intercepts[group]

# Jenerate response variable
Y <- drop(X %*% beta + random_effects + rnorm(n))

# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  group = group,
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)

```

### BRMS

```{r LinearMixedEffectsModels_brms_stan_n1000_p5_J50, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_brms_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group, M_1 = 1, Z_1_1 = rep(1, n), prior_only = FALSE)# Z_1_1 is 1 as this is a random intercept model

LinearMixedEffectsModels_brms_sampling <- sampling(object = LinearMixedEffectsModels_brms_stan, data = LinearMixedEffectsModels_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, seed = 123, control = list(adapt_delta = 0.95)

)
LinearMixedEffectsModels_brms_params <- extract(LinearMixedEffectsModels_brms_sampling)

LinearMixedEffectsModels_brms_sampling_params <- rstan::get_sampler_params(LinearMixedEffectsModels_brms_sampling)

colMeans(LinearMixedEffectsModels_brms_sampling_params[[1]])

```


```{r mbm_LinearMixedEffectsModels_stan_n1000_p5_J50, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_naive_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)
LinearMixedEffectsModels_brms_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group, M_1 = 1, Z_1_1 = rep(1, n), prior_only = FALSE)
LinearMixedEffectsModels_SuffStat_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)

REM_mbm_n1000_p5_J50 <- microbenchmark(
Vectorised = sampling(object = LinearMixedEffectsModels_naive_stan, data = LinearMixedEffectsModels_naive_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
BRMS = sampling(object = LinearMixedEffectsModels_brms_stan, data = LinearMixedEffectsModels_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
SuffStat = sampling(object = LinearMixedEffectsModels_SuffStat_stan, data = LinearMixedEffectsModels_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)),
rstandarm = LinearMixedEffectsModels_rstanarm_sampling <-
  stan_lmer(
    Y ~ X + (1 | group) + 0,
    data = data_rstanarm,
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    adapt_delta = 0.95,
    refresh = 0
  ),
times = 25, unit = "seconds"
)


```

```{r mbm_LinearMixedEffectsModels_stan_n1000_p5_J50_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

REM_mbm_n1000_p5_J50

```

## microbench comparison - n1000, p5 J250

### Simulating Data

```{r mbm_sim_data_n1000_p5_J250, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

# Set seed for reproducibility
set.seed(123)

# Number of observations
n <- 1000
# Number of predictors
p <- 5
# Number of groups
J <- 250

# Jenerate random predictors
X <- matrix(rnorm(n * p), n, p)

# Define true coefficients
beta <- c(1, 2, -1, rep(0, p - 3))  # Only some predictors are non-zero

# Jenerate group indicators
group <- sample(1:J, n, replace = TRUE)
# Jenerate group-level effects
group_intercepts <- rnorm(J, mean = 0, sd = 1)
random_effects <- group_intercepts[group]

# Jenerate response variable
Y <- drop(X %*% beta + random_effects + rnorm(n))

# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  group = group,
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)

```


```{r mbm_LinearMixedEffectsModels_stan_n1000_p5_J250, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

LinearMixedEffectsModels_naive_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)
LinearMixedEffectsModels_brms_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group, M_1 = 1, Z_1_1 = rep(1, n), prior_only = FALSE)
LinearMixedEffectsModels_SuffStat_data <- list(N = n, Y = Y, K = p, X = X, N_1 = J, J_1 = group)

REM_mbm_n1000_p5_J250 <- microbenchmark(
Vectorised = sampling(object = LinearMixedEffectsModels_naive_stan, data = LinearMixedEffectsModels_naive_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
BRMS = sampling(object = LinearMixedEffectsModels_brms_stan, data = LinearMixedEffectsModels_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)), 
SuffStat = sampling(object = LinearMixedEffectsModels_SuffStat_stan, data = LinearMixedEffectsModels_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0, control = list(adapt_delta = 0.95)),
rstandarm = LinearMixedEffectsModels_rstanarm_sampling <-
  stan_lmer(
    Y ~ X + (1 | group) + 0,
    data = data_rstanarm,
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    adapt_delta = 0.95,
    refresh = 0
  ),
times = 25, unit = "seconds"
)


```

```{r mbm_LinearMixedEffectsModels_stan_n1000_p5_J250_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

REM_mbm_n1000_p5_J250

```

```{r mbm_LinearMixedEffectsModels_stan_final_plot_P, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

REM_mbm_n1000_p5_J5_summary <- summary(REM_mbm_n1000_p5_J5)

REM_mbm_n1000_p5_J5_summary[["n"]] <- 1000
REM_mbm_n1000_p5_J5_summary[["J"]] <- 5

REM_mbm_n1000_p5_J50_summary <- summary(REM_mbm_n1000_p5_J50)

REM_mbm_n1000_p5_J50_summary[["n"]] <- 1000
REM_mbm_n1000_p5_J50_summary[["J"]] <- 50

REM_mbm_n1000_p5_J250_summary <- summary(REM_mbm_n1000_p5_J250)

REM_mbm_n1000_p5_J250_summary[["n"]] <- 1000
REM_mbm_n1000_p5_J250_summary[["J"]] <- 250

plot_df_summary <- dplyr::bind_rows(REM_mbm_n1000_p5_J5_summary, REM_mbm_n1000_p5_J50_summary, REM_mbm_n1000_p5_J250_summary)

plot_df_summary["expr"] <- rep(c("vectorised", "brms", "sufficient statistics", "rstanarm"), 3)


REM_plot_P <- ggplot(plot_df_summary, aes(x = factor(J), y = median, colour = expr)) +
    geom_crossbar(aes(ymin = min, ymax = max), position = position_dodge(0.5)) + 
    labs(title = "Linear mixed effects model: $n = 1000$, $p = 5$",
         x = "$J$",
         y = "Time (seconds)") +
    theme_minimal() +
    scale_color_brewer("Method", palette = "Set1") +
    theme(legend.position = "bottom")

REM_plot_P

REM_plot_P_log <- ggplot(plot_df_summary, aes(x = factor(J), y = log(median), colour = expr)) +
    geom_crossbar(aes(ymin = log(min), ymax = log(max)), position = position_dodge(0.5)) + 
    labs(title = "Linear mixed effects model: $n = 1000$, $p = 5$",
         x = "$J$",
         y = "log-Time (log-seconds)") +
    theme_minimal() +
    scale_color_brewer("Method", palette = "Set1") +
    theme(legend.position = "bottom")

REM_plot_P_log



```

```{r mbm_REM_stan_final_plot, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

ggarrange(REM_plot_N_log, REM_plot_P_log, nrow = 1, ncol = 2, common.legend = TRUE, legend="bottom")

```

```{r mbm_REM_stan_final_plot_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 4.5, fig.width = 10, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

ggarrange(REM_plot_N_log, REM_plot_P_log, nrow = 1, ncol = 2, common.legend = TRUE, legend="bottom")


```
