---
title: "Bayesian Linear regression"
author: "Clemens Pilcher and Jack Jewson"
date: "18 Nov 2024"
output: html_document
---

## Preamble {.tabset}

### Working directory

+ Change this to be the directory that the stan files are saved in 

```{r setwd, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

my_dir <- "C:/Users/jjew0003/Documents/BarcelonaProjects/SufficientStatistics/Regression"


```

### Packages

Loading the required packages.

```{r packages, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

library(rstan)
rstan_options(auto_write = TRUE)

library(microbenchmark)
library(brms)

library(rstanarm)

library(ggplot2)
library(ggpubr)
```


### stan

```{r stan, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

setwd(my_dir)

#http://discourse.mc-stan.org/t/stan-recompile-to-avoid-r-from-crashing/2631
BayesianLinearRegression_stan <- rstan::stan_model(file="BayesianLinearRegression.stan")
BayesianLinearRegression_brms_stan <- rstan::stan_model(file="BayesianLinearRegression_brms.stan")
BayesianLinearRegression_SuffStat_stan <- rstan::stan_model(file="BayesianLinearRegression_SuffStat.stan")


```

## n = 100, p = 10

### Simulating Data

```{r sim_data_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

n <- 100
p <- 10

# Generate synthetic data
set.seed(123)  # For reproducibility

# Predictor matrix X
X <- matrix(rnorm(n * p), n, p)

# True regression coefficients
beta <- c(1.5, 2, 2.5, rep(0, p - 3))

# Generate response variable Y with noise
Y <- X[,1] * beta[1] + X[,2] * beta[2] + X[,3] * beta[3] + rnorm(n)
beta



```

### BRMS code

```{r brms, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}


formula <- bf(Y ~ X1 + X2 + X3 + X4 + X5 + X6 + X7 + X8 + X9 + X10 + 0)

# Create the data frame
data_brms <- data.frame(
  Y = Y,          # Response variable
  N = n,          # Number of observations
  P = p           # Number of predictors
)

for (i in 1:p) {
  col_name <- paste0("X", i)
  data_brms[[col_name]] <- X[, i]
}

fit <- brms::brm(formula, data = data_brms, iter = 1, refresh = 0, silent = 0, prior = prior(normal(0, 10), class = b))


brms::stancode(fit)

```

### Vectorised stan manual

```{r BayesianLinearRegression_stan_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

BayesianLinearRegression_data <- list(N = n, Y = Y, K = p, X = X)

BayesianLinearRegression_sampling <- sampling(object = BayesianLinearRegression_stan, data = BayesianLinearRegression_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, seed = 123

)
BayesianLinearRegression_params <- extract(BayesianLinearRegression_sampling)

```


### BRMS

```{r BayesianLinearRegression_brms_stan_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

BayesianLinearRegression_brms_data <- list(N = n, Y = Y, K = p, X = X, prior_only = FALSE)

BayesianLinearRegression_brms_sampling <- sampling(object = BayesianLinearRegression_brms_stan, data = BayesianLinearRegression_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, seed = 123

)
BayesianLinearRegression_brms_params <- extract(BayesianLinearRegression_brms_sampling)

```

### sufficieint statistics

```{r BayesianLinearRegression_SuffStat_stan_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

BayesianLinearRegression_SuffStat_data <- list(N = n, Y = Y, K = p, X = X)

BayesianLinearRegression_SuffStat_sampling <- sampling(object = BayesianLinearRegression_SuffStat_stan, data = BayesianLinearRegression_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, seed = 123

)
BayesianLinearRegression_SuffStat_params <- extract(BayesianLinearRegression_SuffStat_sampling)

```

### rstanarm

https://cran.r-project.org/web/packages/rstanarm/vignettes/lm.html

```{r BayesianLinearRegression_rstanarm_stan_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)


BayesianLinearRegression_rstanarm_sampling <-
  stan_glm(
    Y ~ X + 0,
    data = data_rstanarm,
    family = gaussian(),
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    seed = 123
  )

BayesianLinearRegression_rstanarm_params <- as.matrix(BayesianLinearRegression_rstanarm_sampling)

```

### Posterior Comparison

```{r BayesianLinearRegression_brms_SuffStat_stan_n100_p10_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

for(j in 1:p){
  plot(density(BayesianLinearRegression_params$b[,j]), xlab = paste("beta", j), ylab = "Density", lwd = 3)
  lines(density(BayesianLinearRegression_brms_params$b[,j]), lwd = 3, col = "darkgrey")
  lines(density(BayesianLinearRegression_SuffStat_params$b[,j]), lwd = 3, col = "brown")
  lines(density(BayesianLinearRegression_rstanarm_params[,j]), lwd = 3, col = "pink")
}


plot(density(BayesianLinearRegression_params$sigma), xlab = "sigma", ylab = "Density", lwd = 3)
lines(density(BayesianLinearRegression_brms_params$sigma), lwd = 3, col = "darkgrey")
lines(density(BayesianLinearRegression_SuffStat_params$sigma), lwd = 3, col = "brown")
lines(density(BayesianLinearRegression_rstanarm_params[,p+1]), lwd = 3, col = "pink")
```

```{r BayesianLinearRegression_brms_SuffStat_stan_n100_p10_diag_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
#par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
#par(mgp = c(2.15, 1, 0))
#par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)
par(mar = c(4, 4.3, 0.5, 0.5)) # bottom, left, top, right
par(mgp = c(2.75, 1.05, 0))
par(cex.lab = 1.875, cex.axis = 1.875, cex.main = 1.875)

library(paletteer)
greys <- paletteer_d("RColorBrewer::Greys")

for(j in 1:p){
  plot(density(BayesianLinearRegression_params$b[,j]), xlab = paste0("$\\beta_{", j, "}$"), ylab = "Density", lwd = 4, col = greys[3], main = "")#, main = paste0("Bayesian linear regression $n = 100$ $p = 10$"))
  lines(density(BayesianLinearRegression_brms_params$b[,j]), lwd = 4, col = greys[9], lty = 2)
  lines(density(BayesianLinearRegression_SuffStat_params$b[,j]), lwd = 4, col = greys[5], lty = 3)
  lines(density(BayesianLinearRegression_rstanarm_params[,j]), lwd = 4, col = greys[7], lty = 4)
    if(j == 1){
      legend("topleft", c("brms", "rstanarm", "suff-stat", "vect"), col = c(greys[9], greys[7], greys[5], greys[3]), lwd = rep(4, 4), lty = c(2, 4, 3, 1), bty = "n", cex = 1.5)
  }
}


plot(density(BayesianLinearRegression_params$sigma), xlab = "$\\sigma$", ylab = "Density", lwd = 4, col = greys[3], main = "")#, main = paste0("Bayesian linear regression $n = 100$ $p = 10$"))
lines(density(BayesianLinearRegression_brms_params$sigma), lwd = 4, col = greys[9], lty = 2)
lines(density(BayesianLinearRegression_SuffStat_params$sigma), lwd = 4, col = greys[5], lty = 3)
lines(density(BayesianLinearRegression_rstanarm_params[,p+1]), lwd = 4, col = greys[7], lty = 4)
```

## microbench comparison - n100, p10

### Simulating Data

```{r mbm_sim_data_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

n <- 100
p <- 10

# Generate synthetic data
set.seed(123)  # For reproducibility

# Predictor matrix X
X <- matrix(rnorm(n * p), n, p)

# True regression coefficients
beta <- c(1.5, 2, 2.5, rep(0, p - 3))

# Generate response variable Y with noise
Y <- X[,1] * beta[1] + X[,2] * beta[2] + X[,3] * beta[3] + rnorm(n)
beta

# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)


```


```{r mbm_BayesianLinearRegression_stan_n100_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

BayesianLinearRegression_data <- list(N = n, Y = Y, K = p, X = X)
BayesianLinearRegression_brms_data <- list(N = n, Y = Y, K = p, X = X, prior_only = FALSE)
BayesianLinearRegression_SuffStat_data <- list(N = n, Y = Y, K = p, X = X)

BLR_mbm_n100_p10 <- microbenchmark(
Vectorised = sampling(object = BayesianLinearRegression_stan, data = BayesianLinearRegression_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
BRMS = sampling(object = BayesianLinearRegression_brms_stan, data = BayesianLinearRegression_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
SuffStat = sampling(object = BayesianLinearRegression_SuffStat_stan, data = BayesianLinearRegression_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0),
rstanarm = stan_glm(
    Y ~ X + 0,
    data = data_rstanarm,
    family = gaussian(),
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    refresh = 0
  ), times = 25, unit = "seconds"
)

```

```{r mbm_BayesianLinearRegression_stan_n100_p10_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

BLR_mbm_n100_p10

```

## microbench comparison - n1000, p10

### Simulating Data

```{r mbm_sim_data_n1000_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

n <- 1000
p <- 10

# Generate synthetic data
set.seed(123)  # For reproducibility

# Predictor matrix X
X <- matrix(rnorm(n * p), n, p)

# True regression coefficients
beta <- c(1.5, 2, 2.5, rep(0, p - 3))

# Generate response variable Y with noise
Y <- X[,1] * beta[1] + X[,2] * beta[2] + X[,3] * beta[3] + rnorm(n)
beta

# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)


```


```{r mbm_BayesianLinearRegression_stan_n1000_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

BayesianLinearRegression_data <- list(N = n, Y = Y, K = p, X = X)
BayesianLinearRegression_brms_data <- list(N = n, Y = Y, K = p, X = X, prior_only = FALSE)

BayesianLinearRegression_SuffStat_data <- list(N = n, Y = Y, K = p, X = X)

BLR_mbm_n1000_p10 <- microbenchmark(
Vectorised = sampling(object = BayesianLinearRegression_stan, data = BayesianLinearRegression_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
BRMS = sampling(object = BayesianLinearRegression_brms_stan, data = BayesianLinearRegression_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
SuffStat = sampling(object = BayesianLinearRegression_SuffStat_stan, data = BayesianLinearRegression_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0),
rstanarm = stan_glm(
    Y ~ X + 0,
    data = data_rstanarm,
    family = gaussian(),
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    seed = 123,
    refresh = 0
  ), times = 25, unit = "seconds"
)


```

```{r mbm_BayesianLinearRegression_stan_n1000_p10_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

BLR_mbm_n1000_p10

```

## microbench comparison - n10000, p10

### Simulating Data

```{r mbm_sim_data_n10000_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

n <- 10000
p <- 10

# Generate synthetic data
set.seed(123)  # For reproducibility

# Predictor matrix X
X <- matrix(rnorm(n * p), n, p)

# True regression coefficients
beta <- c(1.5, 2, 2.5, rep(0, p - 3))

# Generate response variable Y with noise
Y <- X[,1] * beta[1] + X[,2] * beta[2] + X[,3] * beta[3] + rnorm(n)
beta

# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)

```


```{r mbm_BayesianLinearRegression_stan_n10000_p10, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

BayesianLinearRegression_data <- list(N = n, Y = Y, K = p, X = X)
BayesianLinearRegression_brms_data <- list(N = n, Y = Y, K = p, X = X, prior_only = FALSE)

BayesianLinearRegression_SuffStat_data <- list(N = n, Y = Y, K = p, X = X)

BLR_mbm_n10000_p10 <- microbenchmark(
Vectorised = sampling(object = BayesianLinearRegression_stan, data = BayesianLinearRegression_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
BRMS = sampling(object = BayesianLinearRegression_brms_stan, data = BayesianLinearRegression_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
SuffStat = sampling(object = BayesianLinearRegression_SuffStat_stan, data = BayesianLinearRegression_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0),
rstanarm = stan_glm(
    Y ~ X + 0,
    data = data_rstanarm,
    family = gaussian(),
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    seed = 123,
    refresh = 0
  ), times = 25, unit = "seconds"
)



```

```{r mbm_BayesianLinearRegression_stan_n10000_p10_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

BLR_mbm_n10000_p10

```

```{r mbm_BayesianLinearRegression_stan_final_plot_N, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

BLR_mbm_n100_p10_summary <- summary(BLR_mbm_n100_p10)

BLR_mbm_n100_p10_summary[["n"]] <- 100
BLR_mbm_n100_p10_summary[["p"]] <- 10

BLR_mbm_n1000_p10_summary <- summary(BLR_mbm_n1000_p10)

BLR_mbm_n1000_p10_summary[["n"]] <- 1000
BLR_mbm_n1000_p10_summary[["p"]] <- 10

BLR_mbm_n10000_p10_summary <- summary(BLR_mbm_n10000_p10)

BLR_mbm_n10000_p10_summary[["n"]] <- 10000
BLR_mbm_n10000_p10_summary[["p"]] <- 10

plot_df_summary <- dplyr::bind_rows(BLR_mbm_n100_p10_summary, BLR_mbm_n1000_p10_summary, BLR_mbm_n10000_p10_summary)

plot_df_summary["expr"] <- rep(c("vectorised", "brms", "sufficient statistics", "rstanarm"), 3)


BLR_plot_N <- ggplot(plot_df_summary, aes(x = factor(n), y = median, colour = expr)) +
    geom_crossbar(aes(ymin = min, ymax = max), position = position_dodge(0.5)) + 
    labs(title = "Linear regression: $p = 10$",
         x = "$n$",
         y = "Time (seconds)") +
    theme_minimal() +
    scale_color_brewer("Method", palette = "Set1") +
    theme(legend.position = "bottom")

BLR_plot_N

BLR_plot_N_log <- ggplot(plot_df_summary, aes(x = factor(n), y = log(median), colour = expr)) +
    geom_crossbar(aes(ymin = log(min), ymax = log(max)), position = position_dodge(0.5)) + 
    labs(title = "Linear regression: $p = 10$",
         x = "$n$",
         y = "log-Time (log-seconds)") +
    theme_minimal() +
    scale_color_brewer("Method", palette = "Set1") +
    theme(legend.position = "bottom")

BLR_plot_N_log


```


## microbench comparison - n1000, p100

### Simulating Data

```{r mbm_sim_data_n1000_p100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

n <- 1000
p <- 100

# Generate synthetic data
set.seed(123)  # For reproducibility

# Predictor matrix X
X <- matrix(rnorm(n * p), n, p)

# True regression coefficients
beta <- c(1.5, 2, 2.5, rep(0, p - 3))

# Generate response variable Y with noise
Y <- X[,1] * beta[1] + X[,2] * beta[2] + X[,3] * beta[3] + rnorm(n)
beta

# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)


```


```{r mbm_BayesianLinearRegression_stan_n1000_p100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

BayesianLinearRegression_data <- list(N = n, Y = Y, K = p, X = X)
BayesianLinearRegression_brms_data <- list(N = n, Y = Y, K = p, X = X, prior_only = FALSE)

BayesianLinearRegression_SuffStat_data <- list(N = n, Y = Y, K = p, X = X)

BLR_mbm_n1000_p100 <- microbenchmark(
Vectorised = sampling(object = BayesianLinearRegression_stan, data = BayesianLinearRegression_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
BRMS = sampling(object = BayesianLinearRegression_brms_stan, data = BayesianLinearRegression_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
SuffStat = sampling(object = BayesianLinearRegression_SuffStat_stan, data = BayesianLinearRegression_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0),
rstanarm = stan_glm(
    Y ~ X + 0,
    data = data_rstanarm,
    family = gaussian(),
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    seed = 123,
    refresh = 0
  ), times = 25, unit = "seconds"
)


```

```{r mbm_BayesianLinearRegression_stan_n1000_p100_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

BLR_mbm_n1000_p100

```

## microbench comparison - n1000, p500

### Simulating Data

```{r mbm_sim_data_n1000_p500, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

n <- 1000
p <- 500

# Generate synthetic data
set.seed(123)  # For reproducibility

# Predictor matrix X
X <- matrix(rnorm(n * p), n, p)

# True regression coefficients
beta <- c(1.5, 2, 2.5, rep(0, p - 3))

# Generate response variable Y with noise
Y <- X[,1] * beta[1] + X[,2] * beta[2] + X[,3] * beta[3] + rnorm(n)
beta

# Create the data frame
data_rstanarm <- data.frame(
  Y = Y,          # Response variable
  X = X,
  N = n,          # Number of observations
  P = p           # Number of predictors
)

```


```{r mbm_BayesianLinearRegression_stan_n1000_p500, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

iterations <- 5000
warmup <- 1000

BayesianLinearRegression_data <- list(N = n, Y = Y, K = p, X = X)
BayesianLinearRegression_brms_data <- list(N = n, Y = Y, K = p, X = X, prior_only = FALSE)

BayesianLinearRegression_SuffStat_data <- list(N = n, Y = Y, K = p, X = X)

BLR_mbm_n1000_p500 <- microbenchmark(
Vectorised = sampling(object = BayesianLinearRegression_stan, data = BayesianLinearRegression_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
BRMS = sampling(object = BayesianLinearRegression_brms_stan, data = BayesianLinearRegression_brms_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0), 
SuffStat = sampling(object = BayesianLinearRegression_SuffStat_stan, data = BayesianLinearRegression_SuffStat_data, iter = iterations + warmup, warmup = warmup, chains = 1, cores = 1, refresh = 0),
rstanarm = stan_glm(
    Y ~ X + 0,
    data = data_rstanarm,
    family = gaussian(),
    prior = normal(0, 10),
    prior_aux = student_t(3, 0, 3.7),
    iter = iterations + warmup, 
    warmup = warmup,
    chains = 1,
    cores = 1,
    seed = 123,
    refresh = 0
  ), times = 25, unit = "seconds"
)


```

```{r mbm_BayesianLinearRegression_stan_final_plot_P, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

BLR_mbm_n1000_p100_summary <- summary(BLR_mbm_n1000_p100)

BLR_mbm_n1000_p100_summary[["n"]] <- 1000
BLR_mbm_n1000_p100_summary[["p"]] <- 100


BLR_mbm_n1000_p500_summary <- summary(BLR_mbm_n1000_p500)

BLR_mbm_n1000_p500_summary[["n"]] <- 1000
BLR_mbm_n1000_p500_summary[["p"]] <- 500


plot_df_summary <- dplyr::bind_rows(BLR_mbm_n1000_p10_summary, BLR_mbm_n1000_p100_summary, BLR_mbm_n1000_p500_summary)

plot_df_summary["expr"] <- rep(c("vectorised", "brms", "sufficient statistics", "rstanarm"), 3)


BLR_plot_P <- ggplot(plot_df_summary, aes(x = factor(p), y = median, colour = expr)) +
    geom_crossbar(aes(ymin = min, ymax = max), position = position_dodge(0.5)) + 
    labs(title = "Linear regression: $n = 1000$",
         x = "$p$",
         y = "Time (seconds)") +
    theme_minimal() +
    scale_color_brewer("Method", palette = "Set1") +
    theme(legend.position = "bottom")

BLR_plot_P

BLR_plot_P_log <- ggplot(plot_df_summary, aes(x = factor(p), y = log(median), colour = expr)) +
    geom_crossbar(aes(ymin = log(min), ymax = log(max)), position = position_dodge(0.5)) + 
    labs(title = "Linear regression: $n = 1000$",
         x = "$p$",
         y = "log-Time (log-seconds)") +
    theme_minimal() +
    scale_color_brewer("Method", palette = "Set1") +
    theme(legend.position = "bottom")

BLR_plot_P_log

```

```{r mbm_BayesianLinearRegression_stan_final_plot, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

ggarrange(BLR_plot_N_log, BLR_plot_P_log, nrow = 1, ncol = 2, common.legend = TRUE, legend="bottom")

```

```{r mbm_BayesianLinearRegression_stan_final_plot_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 4.5, fig.width = 10, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

ggarrange(BLR_plot_N_log, BLR_plot_P_log, nrow = 1, ncol = 2, common.legend = TRUE, legend="bottom")


```
